DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-02-26 rebuttal.tex

% \nati{@michael, how much shall we say here?}
% \mdeff{I like to be open. It's mostly written in the paper anyway.}

\subsection{}
\begin{mdframed}[style=comment]
Thanks to the softmax, the output $\bf{y}\in\mathbb{R}^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the probability that the input sample belongs to class $i$.

- This is a common misconception which is incorrect and needs restating. It is *not* a probability distribution for the class, rather it is a discretised conditional distribution for the class given both the data and the weights and biases of the trained network. One way to see that the value of $y_i$ cannot be considered a probability (which implies P(y|x), i.e. the probability of a class given the data) is that if the network is untrained, would you retrieve back the correct probability? It's wholly dependent on the network.
\end{mdframed}

Thanks for making it precise. We completely agree and updated the manuscript accordingly.

% \nati{By the way, this mean that the reviewer is knowledgeable with ML, and may be Bayesian. He might be working on another spherical approach.}
% \mdeff{The guy likes to be precise.}

### 2019-02-26 scnn.tex
comment 2.6

The softmax layer is the last layer in a neural network engineered for classification. Given the output $\x \in \R^{N_{classes}}$ of the last $FC$ (or $ST$), called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
\begin{equation*}
	y_i = \frac{\exp(x_i)}{\sum_{j=1}^{N_{classes}} \exp(x_j)} \in [0, 1], \ \forall i \in [N_{classes}],
\end{equation*}
where $N_{classes}$ is the number of classes to discriminate. \nati{Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the confidence of the network that the input sample belongs to class $i$. Note that in general, this probability distribution does not correspond to the true posterior distribution $p(y|x)$.} This last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.

@@

A first approach, explored by \citep{boomsma2017spherical} for molecular modeling and \citep{su2017sphericalconv, coors2018spherenet} for omnidirectional imaging, is to use a 2D CNN on a discretization of the sphere that is a grid, such as the equirectangular projection (\figref{sphere_grids}, left panel), or a set of grids, such as the cubed-sphere defined by~\citep{ronchi1996cubed} (\figref{sphere_grids},  middle panel).
As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, which makes it computationally efficient.
This approach is applicable to the many pixelizations that are based on a regular subdivision of a base polyhedron, such as HEALPix. Each base polyhedron then forms a grid.
Care has to be taken to handle boundary conditions: for example by padding a grid with the content of the opposite side (equirectangular) or of the neighboring grids (cubed-sphere, HEALPix). That incurs some computational losses.
For samplings that are not equal area, such as the equirectangular projection, the convolution operation should be adjusted to take the induced distortion into account \citep{su2017sphericalconv, coors2018spherenet}.

>>>>

The softmax layer is the last layer in a neural network engineered for classification. Given the output $\x \in \R^{N_{classes}}$ of the last $FC$ (or $ST$), called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
\begin{equation*}
	y_i = \frac{\exp(x_i)}{\sum_{j=1}^{N_{classes}} \exp(x_j)} \in [0, 1], \ \forall i \in [N_{classes}],
\end{equation*}
where $N_{classes}$ is the number of classes to discriminate.
Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a discretised conditional distribution for the class given the data and trained parameters.
That is, $y_i$ is the confidence of the network that the input sample belongs to class $i$.
% Note that in general, this probability distribution does not correspond to the true posterior distribution $p(y|x)$.
This last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.

@@

A first approach, explored by \citep{boomsma2017spherical} for molecular modeling and \citep{su2017sphericalconv, coors2018spherenet} for omnidirectional imaging, is to use a 2D CNN on a discretisation of the sphere that is a grid, such as the equirectangular projection (\figref{sphere_grids}, left panel), or a set of grids, such as the cubed-sphere defined by~\citep{ronchi1996cubed} (\figref{sphere_grids},  middle panel).
As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, which makes it computationally efficient.
This approach is applicable to the many pixelizations that are based on a regular subdivision of a base polyhedron, such as HEALPix. Each base polyhedron then forms a grid.
Care has to be taken to handle boundary conditions: for example by padding a grid with the content of the opposite side (equirectangular) or of the neighboring grids (cubed-sphere, HEALPix). That incurs some computational losses.
For samplings that are not equal area, such as the equirectangular projection, the convolution operation should be adjusted to take the induced distortion into account \citep{su2017sphericalconv, coors2018spherenet}.
